Data Science Applied to Ag - Final Project - ML

### 2025-04-26 code/Draft_script.qmd
d

@@

xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune(),  # Maximum depth of each tree
  min_n = tune(),  # Minimum samples required to split a node
  learn_rate = tune()) %>% #Specifying XgBoost as our model type, asking to tune the hyperparameters
  set_engine("xgboost") %>% #specify engine 
  set_mode("regression")  # Set to mode

@@

xgb_grid <- grid_latin_hypercube(
  tree_depth(),
  min_n(),
  learn_rate(),
  trees(),
  size = 10
)

>>>>

Declaration of AI use: the following code chunk was inspired and subsequently modified on the basis of code initially generated by ChatGPT

@@

xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune() # ,  # Maximum depth of each tree
  #min_n = tune(),  # Minimum samples required to split a node
  #learn_rate = tune()
  ) %>% #Specifying XgBoost as our model type, asking to tune the hyperparameters
  set_engine("xgboost") %>% #specify engine 
  set_mode("regression")  # Set to mode

@@

xgb_grid <- grid_latin_hypercube(
  trees(),
  tree_depth(),
  #min_n(),
  #learn_rate(),
  size = 10
)
